Plots and tables summarizing results of Poisson simulations

### 2019-11-13 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

```{r load-functions}
source("../code/poisson.functions.R")
source("../code/signals.R")
```

@@

```{r bumps-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.b.1   <- colMeans(rbind(mise.hf.ti.r.4.b.1,
                                     mise.hf.ti.r.5.b.1,
                                     mise.hf.ti.r.6.b.1,
                                     mise.hf.ti.r.7.b.1))
mise.hf.ti.r.b.8   <- colMeans(rbind(mise.hf.ti.r.4.b.8,
                                     mise.hf.ti.r.5.b.8,
                                     mise.hf.ti.r.6.b.8,
									 mise.hf.ti.r.7.b.8))
mise.hf.ti.r.b.128 <- colMeans(rbind(mise.hf.ti.r.4.b.128,
									 mise.hf.ti.r.5.b.128,
									 mise.hf.ti.r.6.b.128,
									 mise.hf.ti.r.7.b.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.b.1,mise.BMSM.b.1,mise.ash.b.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.b.8,mise.BMSM.b.8,mise.ash.b.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.b.128,mise.BMSM.b.128,mise.ash.b.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

>>>>

```{r load-functions}
source("../code/signals.R")
source("../code/poisson.functions.R")
```

@@

```{r bumps-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.b.1   <- colMeans(rbind(mise.hf.ti.r.4.b.1,
                                     mise.hf.ti.r.5.b.1,
                                     mise.hf.ti.r.6.b.1,
                                     mise.hf.ti.r.7.b.1))
mise.hf.ti.r.b.8   <- colMeans(rbind(mise.hf.ti.r.4.b.8,
                                     mise.hf.ti.r.5.b.8,
                                     mise.hf.ti.r.6.b.8,
									 mise.hf.ti.r.7.b.8))
mise.hf.ti.r.b.128 <- colMeans(rbind(mise.hf.ti.r.4.b.128,
									 mise.hf.ti.r.5.b.128,
									 mise.hf.ti.r.6.b.128,
									 mise.hf.ti.r.7.b.128))
pdat.hf.1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.1,
                                         BMSM        = mise.BMSM.b.1,
		  						         SMASH       = mise.ash.b.1))
pdat.hf.8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.8,
                                         BMSM        = mise.BMSM.b.8,
				   				         SMASH       = mise.ash.b.8))
pdat.hf.128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.128,
                                         BMSM        = mise.BMSM.b.128,
									     SMASH       = mise.ash.b.128))
create.violin.plots(pdat.hf.1,pdat.hf.8,pdat.hf.128)
```

Combined results
----------------

*Create plot showing combined results here.*
